---
title: "Reproducible Research: Peer Assessment 1"
author: "Jumadi"
date: "July 11, 2019"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data

```{r, echo=TRUE}

library(data.table)
library(dplyr)
library(ggplot2)

data <- read.csv('activity.csv')
str(data)
data$date <- as.Date(data$date, format="%Y-%m-%d")
head(data)

```

##What is mean total number of steps taken per day?


```{r, echo=TRUE}
sum_data <- data %>% 
  group_by(date) %>% 
  summarise(total_steps = sum(steps),
            mean_steps = mean(steps)            ,
            median_steps = median(steps))

```
**1. Make a histogram of the total number of steps taken each day**

```{r, echo=TRUE}
hist(sum_data$total_steps , main = "Histogram Total Step Each Day" , xlab = "Totoal Step", breaks = 20)
```

**2. Calculate and report the mean and median total number of steps taken per day**
```{r, echo=TRUE}
mean(data$steps , na.rm = 1)
median(data$steps , na.rm = 1)
```


##What is the average daily activity pattern?
**1. Make a time series plot **
```{r, echo=TRUE}
sum_interval <- data%>% 
  group_by(interval) %>% 
  summarize(total_steps= mean(steps, na.rm = 1)) 

ggplot(sum_interval, aes(x=interval, y=total_steps))+ geom_line()
```

**2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps? **

```{r, echo=TRUE}
sum_interval[which(sum_interval$total_steps== max(sum_interval$total_steps)),]
```

##Imputing missing values

**1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)**

```{r, echo=TRUE}
sum(is.na(data))
```

**2. Devise a strategy for filling in all of the missing values in the dataset**
replace Na value with mean for that 5-minute interval
```{r , echo=TRUE}
replacewithmean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
```

**3. Create a new dataset that is equal to the original dataset but with the missing data filled in.**
```{r, echo=TRUE}
meandata <- data%>% group_by(interval) %>% mutate(steps= replacewithmean(steps))
head(meandata)
```

**4. Make a histogram of the total number of steps taken each day**

```{r, echo=TRUE}
sum_meandata <- meandata %>% 
  group_by(date) %>% 
  summarise(total_steps = sum(steps),
            mean_steps = mean(steps)            ,
            median_steps = median(steps))

hist(sum_meandata$total_steps , main = "Histogram Total Step Each Day" , xlab = "Total Steps", breaks = 20)

```

## Differences Mean & Median

```{r}
rbind(mean(data$steps, na.rm = 1,row.names=1) , mean(meandata$steps))
rbind(median(data$steps, na.rm = 1,row.names=1) , median(meandata$steps))
```

There not difference between new data and old data

##Are there differences in activity patterns between weekdays and weekends?

**1. Create a new factor variable in the dataset with two levels -- "weekday" and "weekend" **
```{r, echo=TRUE}
meandata$weekday <- weekdays(meandata$date)
meandata$weekend <- ifelse(meandata$weekday=="Saturday" | meandata$weekday=="Sunday", "Weekend", "Weekday" )
head(meandata)
```

**2. Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) **
```{r, echo=TRUE}
meandataweekendweekday <- aggregate(meandata$steps , by= list(meandata$weekend, meandata$interval), na.omit(mean))
names(meandataweekendweekday) <- c("weekend", "interval", "steps")


ggplot(meandataweekendweekday, aes(x=interval, y=steps, color=weekend)) + geom_line()+
  facet_grid(weekend ~.) + xlab("Interval") + ylab("Mean of Steps") +
  ggtitle("Comparison of Average Number of Steps in Each Interval")
```



